A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-03 main.tex
The first paragraph.

The theory of dependent types was established in 1980s.
$\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types,
which were published in that age.

>>>>

There are many papers on dependent types 
and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
$\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types.
In Advanced Topics in Types and Programming Languages\cite{attapl},
a dependent type system \LLF is designed with the basis of \cite{harper1993framework}.
We adopted \cite{attapl}-like dependent types for \LMD.

One can use depent types in programming languages such as Idris\cite{brady2013idris} or
interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
\red{この段落要らないかも}

Applications of dependent types for real problems were also
